\documentclass[10pt,a4paper]{article}

% ===== PACKAGES =====
\usepackage[a4paper, margin=1.5cm]{geometry} % Set page margins
\usepackage[T1]{fontenc}                      % Font encoding
\usepackage[sfdefault]{FiraSans}              % Use the Fira Sans font for a modern look
\usepackage[hidelinks]{hyperref}              % Clickable links (email, web)
\usepackage{parskip}                          % Use spacing between paragraphs, not indents
\usepackage{titlesec}                         % For custom section headers
\usepackage{enumitem}                         % For customizing lists

% ===== STYLING AND COMMANDS =====

% Section header style: A solid line under the section title
\titleformat{\section}
  {\normalfont\Large\bfseries} % Format
  {}                          % Label
  {0em}                       % Separation
  {}                          % Code before
  [\titlerule\vspace{-4pt}]   % Code after (the line)

% Custom list environment for a tighter, cleaner look
\setlist[itemize]{leftmargin=1.5em, topsep=0.2ex, itemsep=-0.5ex, label=\textbullet}
\setlist[description]{font=\normalfont\bfseries, style=multiline, leftmargin=3.2cm, labelsep=0.5em}


% Remove page numbers
\pagenumbering{gobble}

% Allow for more flexible spacing to prevent text from running into the margin
\emergencystretch=2em

% ===== DOCUMENT START =====
\begin{document}

% ===================================================================
%                                 HEADER
% ===================================================================
\begin{center}
    {\Huge \bfseries Dylan Neve}
\end{center}
\begin{center}
    \href{mailto:neved@tcd.ie}{neved@tcd.ie} | +353 83 473 3284 | Greystones, Co. Wicklow \\
    \href{https://github.com/dylanneve1}{github.com/dylanneve1} | \href{https://linkedin.com/in/dylan-neve}{linkedin.com/in/dylan-neve} | \href{https://g.dev/dylanneve1}{g.dev/dylanneve1}
\end{center}


% ===================================================================
%                                 PROFILE
% ===================================================================
\section*{Profile}
Fourth-year Computer Engineering student on the integrated BAI/MAI pathway at Trinity College Dublin. Achieved First Class Honours (75\%) in Year 3 with proven strengths in operating systems, microprocessor systems, digital design, and data structures. Currently focusing on \textit{Deep Learning \& Computer Vision} and seeking challenging software or systems engineering internships.


% ===================================================================
%                                EDUCATION
% ===================================================================
\section*{Education}
\textbf{Trinity College Dublin} \hfill \textbf{2021--Present} \\
\textit{Computer Engineering (BAI/MAI Integrated Pathway), Year 4}
\begin{itemize}
    \item Year 3 Result: \textbf{First Class Honours (I), 75\%} (60 ECTS awarded).
    \item \textbf{Selected 3rd Year Modules:}
    \begin{itemize}[label={}, leftmargin=1em]
        \item Concurrent Systems \& Operating Systems \hfill \textbf{83\% (I)}
        \item Microprocessor Systems \hfill \textbf{81\% (I)}
        \item Software Design Analysis \hfill \textbf{85\% (I)}
        \item Data Structures \& Algorithms \hfill \textbf{82\% (I)}
        \item Digital Circuits \hfill \textbf{77\% (I)}
        \item Digital Systems Design \hfill \textbf{77\% (I)}
        \item Probability \& Statistics \hfill \textbf{72\% (I)}
    \end{itemize}
    \item \textbf{Key 4th Year Modules:} Deep Learning \& Computer Vision.
\end{itemize}


% ===================================================================
%                             TECHNICAL SKILLS
% ===================================================================
\section*{Technical Skills}
\begin{description}
    \item[Languages] C/C++, Python, Java, Verilog, Assembly, Shell Scripting
    \item[Core Concepts] Operating Systems, Digital Systems, Data Structures \& Algorithms, Computer Networking, FSMs, Combinational \& Sequential Logic, Interrupt Handling
    \item[Tools \& Dev] Linux, Git, Gerrit, CMake, Docker, CI/CD (GitHub Actions), GDB, Valgrind, CLion, Vivado
    \item[Platforms] Raspberry Pi, Raspberry Pi Pico, Arduino, FPGAs (Basys 3), Android (ADB), MATLAB, AutoCAD
    \item[Libraries] OpenCV, OpenGL
\end{description}


% ===================================================================
%                           ACADEMIC PROJECTS
% ===================================================================
\section*{Academic Projects}
\textbf{ARM Assembly Programming on Raspberry Pi Pico} \hfill \textbf{2025} \\
\textit{Technologies: Assembly, C, Raspberry Pi Pico SDK}
\begin{itemize}
    \item As part of a group project, I developed low-level drivers in assembly for a Morse code training game, interfacing with hardware timers and GPIO for button input.
    \item Implemented a robust interrupt service routine (ISR) to handle GPIO events, calculate button press durations, and classify inputs as dots or dashes.
    \item Created a circular buffer in assembly to manage Morse code elements, ensuring efficient data transfer between the ISR and the main C application logic.
\end{itemize}
\medskip
\textbf{Digital Logic System Design on FPGA} \hfill \textbf{2025} \\
\textit{Technologies: Verilog, Vivado, Basys 3 FPGA, XDC}
\begin{itemize}
    \item Designed, implemented, and verified multiple digital systems, including a 6-bit ALU, a 20-bit LFSR, and a Moore FSM for codeword detection.
    \item Managed the complete FPGA workflow: creating modular designs in Verilog, validating with testbenches in Vivado, and deploying to a Basys 3 board.
    \item Mapped system I/O to physical board peripherals (switches, LEDs, 7-segment display) using Xilinx Design Constraints (XDC).
\end{itemize}
\medskip
\textbf{LunarBuggyPy --- Control \& Telemetry Stack (Group Project)} \hfill \textbf{2025} \\
\textit{Technologies: Python, UDP, OpenCV, Raspberry Pi, WireGuard,} \texttt{netem}
\begin{itemize}
    \item Designed a robust, two-part system (\texttt{buggyudp} and \texttt{controludp}) for remote vehicle operation over local and VPN-secured networks.
    \item Implemented efficient, packetised command, video, and telemetry streams over UDP, incorporating network latency and impairment simulation.
    \item Integrated OpenCV for real-time image processing and developed comprehensive bring-up scripts for simplified deployment.
    \item Project Repository: \href{https://github.com/dylanneve1/lunarbuggypy}{github.com/dylanneve1/lunarbuggypy}
\end{itemize}
\medskip
\textbf{Data Structures \& Algorithms Implementations} \hfill \textbf{2024} \\
\textit{Technologies: C, Algorithm Analysis}
\begin{itemize}
    \item Implemented a comprehensive library of fundamental data structures including linked lists, stacks, queues, trees, graphs, and hash tables.
    \item Developed and analysed core sorting, searching, and graph traversal algorithms, documenting complexity trade-offs for each implementation.
\end{itemize}


% ===================================================================
%                                EXPERIENCE
% ===================================================================
\section*{Experience}
\textbf{IT Technician Intern} --- John Sisk \& Sons, Citywest \hfill \textbf{Jun--Aug 2024}
\begin{itemize}
    \item Administered Active Directory users and groups, and deployed laptops at scale using a standardised imaging process, enhancing deployment efficiency.
    \item Resolved over \textbf{400} hardware and software support tickets within strict SLAs.
\end{itemize}
\medskip
\textbf{Kitchen \& Care Assistant} --- Greystones Nursing Home \hfill \textbf{May 2022--May 2023}
\begin{itemize}
    \item Collaborated with nursing staff to manage resident mealtimes, including order taking, food preparation, service, and adherence to hygiene standards.
\end{itemize}
\medskip
\textbf{IT Support Intern} --- DermView Ltd., Carrickmines \hfill \textbf{Jun 2020}
\begin{itemize}
    \item Configured and deployed clinical devices with Mobile Device Management (MDM) software.
\end{itemize}


% ===================================================================
%                        ACHIEVEMENTS & INTERESTS
% ===================================================================
\section*{Achievements \& Interests}
\begin{itemize}
    \item \textbf{Open Source Contribution:} Maintained device trees for PixelExperience (Android 10--14) on Exynos9810, performing kernel backports and implementing runtime resolution switching.
    \item \textbf{Workshops \& Courses:} Completed Google Algorithms Workshop (2024); Former participant in CTYI (Top 5\% in SCAT), studying Computer Science and Medicine.
\end{itemize}

\vfill
\begin{center}
    \small Last updated: September 2025
\end{center}

\end{document}